---
title: "Spatio-temporally biased re-sampling techniques"
author: "Mariana Oliveira, Nuno Moniz, Luis Torgo, Vitor Santos Costa"
date: ""
output:
    html_document:
      toc: true
      toc_depth: 3
      self_contained: TRUE
---

```{r, include=F, warning=F, message=FALSE, results='hide'}
library(tidyverse)
library(knitr)
library(plotly)
library(grid)
library(sf)
library(xts)
library(quantmod)
library(STResamplingDSAA)

opts_chunk$set(eval=T, echo=F, fig.path = "figs/",
               dev=c("png","cairo_ps"), warning=FALSE)

DATA_PATH <- "./extdata/"
RESULTS_PATH <- "./"
UTILS_PATH <- "../R/" # if package not installed

if(!("STResamplingDSAA") %in% installed.packages()){
  tosource <- list.files(UTILS_PATH, full.names = TRUE)
  for(f in tosource) source(f)
}else{
  library(STResamplingDSAA)
}
```

```{r, echo=F, warning=F}
m_labels <- c(rpart="RPART", earth="MARS", ranger="RF")
s_labels <- c(under="RUS", stunder="STRUS", 
              over="ROS", stover="STROS",
              baseline="BASELINE")
d_labels <- c(MESApol=10, NCDCPprec=20,TCEQOozone=30,
              TCEQTtemp=31, TCEQWwind=32, RURALpm10=40,
              BEIJno=50, BEIJpm10=51, BEIJwind=52, BEIJpm25=53)

dataPalette <- c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00','#cab2d6','#6a3d9a')
```

# III. Spatio-Temporal Bias Resampling Strategies

```{r}
load(paste0(DATA_PATH, "dfs.Rdata"))
load(paste0(DATA_PATH, "inds_df.Rdata"))
```

## A. Algorithms

```{r surfaces-2d, eval=T, warning=F, fig.width=8.5, fig.height=6}
dfnm <- "TCEQTtemp"
 
stations <- data_list[[dfnm]]$stations
stations$station <- paste0("L", data_list[[dfnm]]$stations$station)
  
# reorder stations
coords <- stations %>% sf::st_coordinates(geometry) 
stations <- stations[order(coords[,"X"], coords[,"Y"]),]
stations$new_station <- paste0("L", stringr::str_pad(1:nrow(stations), width=2, side="left", pad="0"))
  
new_names <- stations$new_station
names(new_names) <- stations$station
  
stations$station <- stations$new_station

df <- inds_df[[dfnm]]$df[,c("station", "time", "value")]
df$station <- paste0("L", df$station)
df$station <- as.factor(new_names[df$station])
 
df$time <- as.Date(df$time)
x <- sample_wts(value~., df, alpha=0.5, uba::phi.control(df$value), rel.thr=0.9, epsilon=1E-4, site_id="station", time="time", sites_sf = stations)
df <- cbind(df, x)
  
df_l <- df %>% gather(variable, value, -station,-time) %>%
      mutate(time=norm_scale(as.numeric(time)))
  
labels <- c(phi="\u03d5", space_wts="W\u1d38", time_wts="W\u1d40", stprob_add="W")
  
gg1 <- ggplot(df_l %>%
           filter(variable %in% c("phi", "space_wts", "time_wts", "stprob_add")) %>%
           mutate(variable=labels[variable],
             variable=factor(variable, levels=c("\u03d5", "W","W\u1d38","W\u1d40"))), 
           aes(x=time, y=station, fill=value)) +
    geom_tile() + 
    facet_wrap(~variable) + 
    theme(panel.background = element_blank())

print(gg1)
```

**Figure 2**: Heatmaps for data set 31, showing relevance values, $\phi$, spatial weight, $W^L$, temporal weight, $W^T$ and their combination as the spatio-temporal weight, $W$. Each cell in the heatmap corresponds to one observation at a given point in time and location

# IV. Experimental Evaluation

## A. Data and Methods

**Table I**: Real-world data sets

```{r data-desc}
dfs_desc <- t(sapply(data_list, function(x){
  
  tab <- data.frame(ts=length(unique(x$df$time)), ss=length(unique(x$df$station)), true_nr=nrow(x$df))
  tab$nr <- tab$ss*tab$ts
  tab$avail <- tab$true_nr/tab$nr
  
  y <- x$df$value
  ph <- uba::phi.control(y, method="extremes", coef=1.5)
  ls <- uba::loss.control(y)
  phi <- uba::phi(y = y, phi.parms = ph)
  
  tab$perc <- 100*as.numeric( length(which(phi>=0.9)) / length(y) )
  
  as.data.frame(tab)
}))

dfs_desc <- cbind(data.frame(data=d_labels[rownames(dfs_desc)]),
                  apply(dfs_desc,2,unlist))
rownames(dfs_desc) <- NULL
dfs_desc <- dfs_desc[!is.na(dfs_desc$data),-4]
colnames(dfs_desc) <- c("data", "timeIDs", "locIDs", "insts", "avail", "perc_extr")

kable(dfs_desc, digits=2)
```


# V. Results

```{r load-int-results}
load(paste0(RESULTS_PATH, "sumRes_internalTuning.Rdata"))

sumResTab_int$rep <- as.factor(1)

sumResTab_int <- sumResTab_int %>% 
  ungroup() %>%
  mutate(model = as.factor(m_labels[as.character(model)]),
    sampling = as.factor(s_labels[as.character(sampling)]),
    data = as.factor(d_labels[as.character(data)])) %>%
  ungroup()

medResTab_int_all <- sumResTab_int %>%
  ungroup() %>%
  select(-fold) %>%
  group_by(model, data, sampling, rep) %>%
  summarize_all(mean, na.rm=T) %>%
  ungroup()
  
medResTab_int <- medResTab_int_all %>% 
  select(model, data, sampling, F1.u, rep)

medResTab_int_pr <- medResTab_int_all %>%
  select(model, data, sampling, prec.u, rec.u, rep)
```

## B. Tuning parameters

**Figure 5(a)**: Baseline and best $F_1^u$ result achieved for each data set. Top layers present MARS results, followed by RF and RPART. Two columns corresponds to a dataset: a baseline, in gray, and the best result. Under-sampling is shown in shades of purple, over-sampling in orange shades; darker colours indicate bias **(a)** Internally tuned parameters

```{r tuned-best, fig.width=7, fig.height=5}
int_all <- medResTab_int %>% 
  group_by(model, data) %>% 
  filter(sampling!="BASELINE") %>%
  filter(F1.u==max(F1.u, na.rm=T)) %>% 
  select(model, data, sampling, F1.u) %>%
  rename(best=F1.u)

baseline_all_int <- medResTab_int %>% 
  filter(sampling=="BASELINE") %>%
  select(data, model, F1.u) %>%
  rename(baseline=F1.u)

x <- left_join(baseline_all_int, int_all, by=c("model", "data")) %>%
  select(data, model, sampling, baseline, best) %>%
  arrange(data, model)


ggplot(tidyr::gather(x, type, value, baseline, best) %>%
         mutate(sampling=ifelse(type=="baseline", "None", as.character(sampling))),
       aes(x=data, y=value, fill=sampling)) + 
  geom_bar(stat="identity", position = "dodge") +
  facet_grid(model~.) +
  scale_fill_manual(values=c("grey", '#fdb863','#b2abd2', '#e66101','#5e3c99')) +
  ylab("F1.u") +
  xlab("data set")
```

**Table III**: Average ranks of $F_1^u$ per model using tuned parameters

```{r int-avg-ranks-model}
s_order <- c("BASELINE", "ROS", "STROS", "RUS", "STRUS")

avg_ranks <- medResTab_int_all %>%
  group_by(rep, model, data, sampling) %>%
  summarize_at(c("F1.u", "prec.u", "rec.u"), mean, na.rm=T) %>%
  mutate_at(c("F1.u", "prec.u", "rec.u"), funs(r=min_rank(desc(.)))) %>%
  group_by(model, sampling) %>% 
  summarize_at(c("F1.u_r", "prec.u_r", "rec.u_r"), funs(avg=mean(.))) %>%
  gather(metric, avg_rank, -model, -sampling) %>%
  spread(sampling, avg_rank) %>%
  arrange(metric, model) %>%
  filter(metric=="F1.u_r_avg")

kable(avg_ranks[,c("model", s_order)], digits=2)
```

**Table IV**: Average ranks of $F_1^u$ per data set using tuned parameters


```{r int-avg-ranks-data}
avg_ranks <- medResTab_int %>% 
  group_by(rep, model, data, sampling) %>%
  summarize(bestF1.u=max(F1.u, na.rm=T)) %>%
  mutate(r=min_rank(desc(bestF1.u))) %>%
  group_by(data, sampling) %>% 
  summarize(avg_rank=mean(r)) %>%
  spread(sampling, avg_rank)

kable(avg_ranks[,c(1:3,5,4,6)], digits=2)
```


```{r}
int_rank_for_later <- medResTab_int %>% 
  group_by(rep, model, data) %>%
  mutate(r=min_rank(desc(F1.u))) %>%
  group_by(sampling) %>% 
  summarize(avg_rank=mean(r)) %>%
  spread(sampling, avg_rank)
```



## C. Fixing parameters *a priori*

Parameters fixed to $alpha$=0.5, O\%=2 and U\%=0.6.

```{r load-results}
load(paste0(RESULTS_PATH, "sumRes_externalPrequential.Rdata"))
sumResTab$rep <- 1
```

```{r sum-res-exps}
medResTab_reps <- sumResTab %>%
  select(-fold) %>%
  group_by(rep, model, data, sampling) %>%
  summarize_all(mean, na.rm=T) %>%
  rename(method = sampling) %>%
  tidyr::separate(method, c("sampling", "discard", "cperc", "discard2", "alpha"), sep="_", extra="drop", fill="right", remove=FALSE) %>%
  select(-discard, -discard2) %>%
  ungroup() %>%
  mutate(rep = as.factor(rep),
    model = as.factor(m_labels[as.character(model)]),
    sampling = as.factor(s_labels[as.character(sampling)]),
    data = as.factor(d_labels[as.character(data)])) %>%
  mutate_at(vars(one_of("cperc", "alpha")), as.numeric) %>%
  ungroup()

medResTab_all <- medResTab_reps %>%
  group_by(model, data, method, sampling, cperc, alpha) %>%
  select(-rep) %>%
  summarize_all(mean, na.rm=T) %>%
  ungroup()
  
medResTab <- medResTab_all %>% 
  select(model, data, method, sampling, cperc, alpha, F1.u)
  
medResTab_pr <- medResTab_all %>%
  select(model, data, method, sampling, cperc, alpha, prec.u, rec.u)
```

```{r against-baseline, fig.width=7, fig.height=5}
fix_all <- medResTab %>% 
  filter(alpha %in% c(NA,0.5), cperc %in% c(0.6,2)) %>% 
  group_by(model, data) %>% 
  filter(F1.u==max(F1.u, na.rm=T)) %>% 
  select(model, data, method, sampling, F1.u) %>%
  rename(best=F1.u)

baseline_all <- medResTab %>% filter(method=="baseline") %>%
  select(data, model, F1.u) %>%
  rename(baseline=F1.u)

x <- left_join(fix_all, baseline_all, by=c("model", "data")) %>%
  select(data, model, method, sampling, baseline, best) %>%
  arrange(data, model)

ggplot(gather(x, type, value, baseline, best) %>%
         mutate(sampling=ifelse(type=="baseline", "None", as.character(sampling))),
       aes(x=data, y=value, fill=sampling)) + 
  geom_bar(stat="identity", position = "dodge") +
  facet_grid(model~.) +
  scale_fill_manual(values=c("grey", '#fdb863','#b2abd2', '#e66101','#5e3c99')) +
  ylab("F1.u") +
  xlab("data set") +
  ylim(0,1)
```

**Figure 5(b)**: Baseline and best $F_1^u$ result achieved for each data set. Top layers present MARS results, followed by RF and RPART. Two columns corresponds to a dataset: a baseline, in gray, and the best result. Under-sampling is shown in shades of purple, over-sampling in orange shades; darker colours indicate bias **(b)** Fixed parameters

**Table V**: Average ranks of $F_1^u$ per model with fixed parameters

```{r overall-ranks-fixed-oracle-model}
avg_ranks <- medResTab %>% 
  filter(alpha %in% c(NA, 0.5), cperc %in% c(NA,0.6,2)) %>%
  group_by(model, data) %>%
  mutate(r=min_rank(desc(F1.u))) %>%
  group_by(model, sampling) %>% 
  summarize(avg_rank=mean(r)) %>%
  spread(sampling, avg_rank)

kable(avg_ranks[,c(1:3,5,4,6)], digits=2)
```

**Table VI**: Average ranks of $F_1^u$ per data set with fixed parameters

```{r overall-ranks-fixed-oracle-data}

avg_ranks <- medResTab %>% 
  filter(alpha %in% c(NA, 0.5), cperc %in% c(NA,0.6,2)) %>%
  group_by(model, data) %>%
  mutate(r=min_rank(desc(F1.u))) %>%
  group_by(data, sampling) %>% 
  summarize(avg_rank=mean(r)) %>%
  spread(sampling, avg_rank)

kable(avg_ranks[,c(1:3,5,4,6)], digits=2)
```

```{r}
fixed_rank_for_later <- medResTab %>% 
  filter(alpha %in% c(NA, 0.5), cperc %in% c(NA,0.6,2)) %>%
  group_by(model, data) %>%
  mutate(r=min_rank(desc(F1.u))) %>%
  group_by(sampling) %>% 
  summarize(avg_rank=mean(r)) %>%
  spread(sampling, avg_rank)
```

## D. Optimal parametrization

```{r best-all, fig.width=7, fig.height=5}
best_all <- medResTab %>% group_by(model,data) %>% 
  filter(F1.u==max(F1.u, na.rm=T)) %>% 
  select(model, data, method, sampling, F1.u) %>%
  rename(best=F1.u)

baseline_all <- medResTab %>% filter(method=="baseline") %>%
  select(data, model, F1.u) %>%
  rename(baseline=F1.u)

x <- left_join(best_all, baseline_all, by=c("model", "data")) %>%
  select(data, model, method, sampling, baseline, best) %>%
  arrange(data, model)

ggplot(gather(x, type, value, baseline, best) %>%
         mutate(sampling=ifelse(type=="baseline", "None", as.character(sampling))),
       aes(x=data, y=value, fill=sampling)) + 
  geom_bar(stat="identity", position = "dodge") +
  facet_grid(model~.) +
  scale_fill_manual(values=c("grey", '#fdb863','#b2abd2', '#e66101','#5e3c99')) +
  ylab("F1.u") +
  xlab("data set") +
  ylim(0,1)
```

**Figure 5(c)**: Baseline and best $F_1^u$ result achieved for each data set. Top layers present MARS results, followed by RF and RPART. Two columns corresponds to a dataset: a baseline, in gray, and the best result. Under-sampling is shown in shades of purple, over-sampling in orange shades; darker colours indicate bias **(c)** Optimal parameters

**Table VII**: Average ranks of optimal $F_1^u$ results per model

```{r overall-ranks-oracle-model}
avg_ranks <- medResTab %>% 
  group_by(model, data, sampling) %>%
  summarize(bestF1.u=max(F1.u, na.rm=T)) %>%
  group_by(model, data) %>%
  mutate(r=min_rank(desc(bestF1.u))) %>%
  group_by(model, sampling) %>% 
  summarize(avg_rank=mean(r)) %>%
  spread(sampling, avg_rank)

kable(avg_ranks[,c(1:3,5,4,6)], digits=2)
```

**Table VIII**: Average ranks of optimal $F_1^u$ results per data set

```{r overall-ranks-oracle-data}

avg_ranks <- medResTab %>% 
  group_by(model, data, sampling) %>%
  summarize(bestF1.u=max(F1.u, na.rm=T)) %>%
  group_by(model, data) %>%
  mutate(r=min_rank(desc(bestF1.u))) %>%
  group_by(data, sampling) %>% 
  summarize(avg_rank=mean(r)) %>%
  spread(sampling, avg_rank)

kable(avg_ranks[,c(1:3,5,4,6)], digits=2)
```

```{r}
best_rank_for_later <- medResTab %>% 
  group_by(model, data, sampling) %>%
  summarize(bestF1.u=max(F1.u, na.rm=T)) %>%
  group_by(model, data) %>%
  mutate(r=min_rank(desc(bestF1.u))) %>%
  group_by(sampling) %>% 
  summarize(avg_rank=mean(r)) %>%
  spread(sampling, avg_rank)
```

```{r cd-diag-oracle, fig.height=3, fig.width=5}
best <- medResTab %>% 
  group_by(model, data, sampling) %>%
  summarize(bestF1.u=max(F1.u, na.rm=T)) %>%
  tidyr::spread(sampling, bestF1.u) %>%
  as.data.frame()

for(m in unique(best$model)){
  b <- best[which(best$model==m),]
  scmamp::plotCD(b[,c(-1,-2)], cex = 0.8)  
  cat(paste(m, "\n"))
}

best_l <- tidyr::gather(best, key="sampling", value="F1.u", 
                        s_labels)
```

**Figure 6**: Critical difference diagrams for different algorithms

## A. Summary of results

**Table II**: Average ranks of $F_1^u$ results

```{r}
x <- cbind(data.frame(method=c("internally tuned", "fixed arbitrarily a priori", "optimal a posteriori")), bind_rows(int_rank_for_later, bind_rows(fixed_rank_for_later, best_rank_for_later)))

kable(x[,c(1:3,5,4,6)], digits=2)
```

## E. Parameter sensitivity analysis

```{r avg-rank-f1-heatmap, fig.width=6, fig.height=5}
ranks_f1 <- medResTab %>% 
  group_by(model, data) %>% 
  mutate(r=min_rank(desc(F1.u))) %>% 
  group_by(model, method, sampling, cperc, alpha) %>%
  summarize(avg_rank=mean(r,na.rm=T), sd_rank=sd(r,na.rm=T)) %>%
  ungroup() %>%
  mutate(under_or_over = ifelse(sampling=="BASELINE","BASELINE", 
                                ifelse(grepl("OS", sampling), "OS", "US")))

gg <- ggplot(ranks_f1 %>%
         filter(sampling!="BASELINE"), aes(as.character(cperc), as.character(alpha))) +
  geom_tile(aes(fill = avg_rank), color = "white") +
   scale_fill_gradient(low = "white", high = "steelblue",
                      limits=c(10,56),
                      guide=guide_colorbar(title = "r(F1.u)",
                                           reverse=T,
                                           draw.ulim = T,
                                           draw.llim = T,
                                           ticks.colour = "black")) +
  facet_grid(model~under_or_over, scales="free_x") +
  xlab("o / u") +
  ylab("\u03B1") +
  facet_grid(model~under_or_over, scales="free_x") 

print(gg)
```

**Figure 7**: Average $F_1^u$ rank for 60(+1) different parametrizations. Ranks were calculated separately for each learning model and data set before averaging. The baseline was included in rank calculation, but excluded from the graph. Non-biased resampling is denoted by $\alpha=\mathrm{NA}$. Lower ranks correspond to better results

```{r avg-rank-f1-heatmap-alpha, fig.height=3, fig.width=6}
ranks_f1_alpha <- medResTab %>% 
  group_by(model, data, sampling, cperc) %>% 
  mutate(r=min_rank(desc(F1.u))) %>% 
  group_by(sampling, alpha) %>%
  summarize(avg_rank=mean(r,na.rm=T), sd_rank=sd(r,na.rm=T)) %>%
  ungroup() %>%
  mutate(under_or_over = ifelse(sampling=="BASELINE","BASELINE", ifelse(grepl("OS", sampling), "OS", "US")))

text_high <- textGrob("Temporal weights", gp=gpar(fontsize=9, fontface="bold"))
text_low <- textGrob("Spatial weights", gp=gpar(fontsize=9, fontface="bold"))

gg <- ggplot(ranks_f1_alpha %>%
         filter(sampling %in% c("STROS", "STRUS")), aes( alpha, sampling)) +
  geom_tile(aes(fill = avg_rank), color = "white") +
  scale_fill_gradient(low = "white", high = "steelblue", 
                      guide = guide_colorbar(title="r(F1.u)",
                      ticks=T, ticks.colour="black",
                                             draw.ulim = T, draw.llim = T,
                                             reverse=T)) +
  scale_x_continuous(breaks = seq(0,1,0.25)) +
  theme(plot.margin = unit(c(1,1,2,1), "lines")) +
  annotation_custom(text_high,xmin=1,xmax=1,ymin=-0.1,ymax=-0.1) + 
  annotation_custom(text_low,xmin=0,xmax=0,ymin=-0.1,ymax=-0.1)+
  coord_cartesian(clip="off") +
  xlab("\u03B1")

print(gg)
```

**Figure 8**: Average $F_1^u$ rank for 5 different values of $\alpha$. Ranks were calculated separately for each learning model and data set before averaging. Lower ranks correspond to better results

## F. Precision and recall trade-off

```{r avg-rank-prec-heatmap, fig.width=6, fig.height=5}
ranks_pr <- medResTab_pr %>% 
  group_by(model, data) %>% 
  mutate(r_prec=min_rank(desc(prec.u)),
         r_rec=min_rank(desc(rec.u))) %>% 
  group_by(model, method, sampling, cperc, alpha) %>%
  summarize(avg_rank_prec=mean(r_prec,na.rm=T),
            sd_rank_prec=sd(r_prec,na.rm=T),
            avg_rank_rec=mean(r_rec,na.rm=T),
            sd_rank_rec=sd(r_rec,na.rm=T)) %>%
  ungroup() %>%
  mutate(under_or_over = ifelse(sampling=="BASELINE","BASELINE", ifelse(grepl("OS", sampling), "OS", "US")))

gg <- ggplot(ranks_pr %>%
         filter(sampling!="BASELINE"), aes(as.character(cperc), as.character(alpha))) +
  geom_tile(aes(fill = avg_rank_prec), color = "white") +
    scale_fill_gradient(low = "white", high = "steelblue",
                        limits=c(1,61),
                      guide=guide_colorbar(title = "r(Prec.u)",
                                           reverse=T,
                                           draw.ulim = T,
                                           draw.llim = T,
                                           ticks.colour = "black")) +
  xlab("o / u") +
  ylab("\u03B1") +
  facet_grid(model~under_or_over, scales="free_x") #+

print(gg)
```

```{r avg-rank-rec-heatmap, fig.width=6, fig.height=5}
gg <- ggplot(ranks_pr %>%
         filter(sampling!="BASELINE"), aes(as.character(cperc), as.character(alpha))) +
  geom_tile(aes(fill = avg_rank_rec), color = "white") +
    geom_tile(aes(fill = avg_rank_rec), color = "white") +
    scale_fill_gradient(low = "white", high = "steelblue",
                        limits=c(1,61),
                      guide=guide_colorbar(title = "r(Rec.u)",
                                           reverse=T,
                                           draw.ulim = T,
                                           draw.llim = T,
                                           ticks.colour = "black")) +
  xlab("o / u") +
  ylab("\u03B1") +
  facet_grid(model~under_or_over, scales="free_x") #+

print(gg)
```

**Figure 9**: Average precision and recall rank for 60(+1) different parametrizations. Ranks were calculated separately for each learning model and data set before averaging. The baseline was included in rank calculation, but excluded from the graph. Non-biased resampling is denoted by $\alpha=\mathrm{NA}$. Lower ranks correspond to better results **(a)** $prec_{\phi}^{u}$ **(b)** $rec_{\phi}^{u}$

# Appendix

### A. Tuning parameters

**Table A.I**: Mean $F_1^u$ with internally tuned parameters

```{r}
x <- medResTab_int_all %>%
  select(data, model, sampling, F1.u) %>%
  arrange(model, data, sampling) %>%
  tidyr::spread(sampling, F1.u)

kable(x, digits=3)
```

**Table A.II**: Mean $prec_{\phi}^{u}$ with internally tuned parameters

```{r}
x <- medResTab_int_all %>%
  select(data, model, sampling, prec.u) %>%
  arrange(model, data, sampling) %>%
  tidyr::spread(sampling, prec.u)

kable(x, digits=3)
```

**Table A.III**: Mean $rec_{\phi}^{u}$ with internally tuned parameters

```{r}
x <- medResTab_int_all %>%
  select(model, data, sampling, rec.u) %>%
  arrange(model, data, sampling) %>%
  tidyr::spread(sampling, rec.u)

kable(x, digits=3)
```

### B. Fixed parameters

**Table B.I**: Mean $F_1^u$ with fixed parameters

```{r}
x <- medResTab_all %>%
  filter(alpha %in% c(NA, 0.5), cperc %in% c(NA,0.6,2)) %>%
  select(model, data, sampling, F1.u) %>%
  arrange(model, data, sampling) %>%
  tidyr::spread(sampling, F1.u)

kable(x, digits=3)
```

**Table B.II**: Mean $prec_{\phi}^{u}$ with fixed parameters

```{r}
x <- medResTab_all %>%
  filter(alpha %in% c(NA, 0.5), cperc %in% c(NA,0.6,2)) %>%
  select(model, data, sampling, prec.u) %>%
  arrange(model, data, sampling) %>%
  tidyr::spread(sampling, prec.u)

kable(x, digits=3)
```

**Table B.III**: Mean $rec_{\phi}^{u}$ with fixed parameters

```{r}
x <- medResTab_all %>%
  filter(alpha %in% c(NA, 0.5), cperc %in% c(NA,0.6,2)) %>%
  select(model, data, sampling, rec.u) %>%
  arrange(model, data, sampling) %>%
  tidyr::spread(sampling, rec.u)

kable(x, digits=3)
```


### C. Optimal parameters

**Table C.I**: Mean $F_1^u$ with optimal parameters

```{r}
x <- medResTab_all %>%
  group_by(model,data) %>% 
  filter(F1.u==max(F1.u, na.rm=T)) %>% 
  ungroup() %>%
  select(model, data, sampling, cperc, alpha, F1.u) %>%
  arrange(model, data, sampling)

kable(x, digits=3)
```

**Table C.II**: Mean $prec_{\phi}^{u}$ with optimal parameters

```{r}
x <- medResTab_all %>%
  group_by(model,data) %>% 
  filter(F1.u==max(F1.u, na.rm=T)) %>% 
  ungroup() %>%
  select(model, data, sampling, cperc, alpha, prec.u) %>%
  arrange(model, data, sampling)

kable(x, digits=3)
```

**Table C.III**: Mean $rec_{\phi}^{u}$ with optimal parameters

```{r}
x <- medResTab_all %>%
  group_by(model,data) %>% 
  filter(F1.u==max(F1.u, na.rm=T)) %>% 
  ungroup() %>%
  select(model, data, sampling, cperc, alpha, rec.u) %>%
  arrange(model, data, sampling)

kable(x, digits=3)
```

### E. Parameter sensitivity analysis

**Table E.I**: Mean rank with each set of parameters

```{r}
x <- medResTab_all %>%
  select(model, data, sampling, cperc, alpha, F1.u, prec.u, rec.u) %>%
  arrange(model, data, sampling) %>%
  group_by(data, model) %>%
  mutate_at(c("F1.u", "prec.u", "rec.u"), 
            .funs=list(rank=~min_rank(desc(.)))) %>%
  group_by(model, sampling, cperc, alpha) %>%
  summarize_at(paste0(c("F1.u", "prec.u", "rec.u"),"_rank"), .funs=list(avg=~mean(.)))

kable(x, digits=2)
```

### F. Figures in presentation

```{r pres-target-boxplots, eval=T}
inds_df <- inds_df[which(names(inds_df) %in% names(d_labels))]

ys <- lapply(inds_df, function(x) data.frame(value=x$df$value))

ys_l <- ys
names(ys_l) <- as.character(d_labels[names(ys_l)])
for(v in 1:length(ys_l)) ys_l[[v]]$data <- names(ys_l)[v]
ys_l <- bind_rows(ys_l)
  
ggplot(ys_l, aes(x=NA, y=value)) +
  geom_boxplot() + 
  facet_wrap(~data, scales = "free_y", ncol=5) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

```

**Figure F.1**: Boxplot of target variables

```{r pres-df, width=4, height=2}
dfnm <- "BEIJpm25"
 
stations <- data_list[[dfnm]]$stations
stations$station <- paste0("L", data_list[[dfnm]]$stations$station)
  
# reorder stations
coords <- stations %>% sf::st_coordinates(geometry) 
stations <- stations[order(coords[,"X"], coords[,"Y"]),]
stations$new_station <- paste0("L", stringr::str_pad(1:nrow(stations), width=2, side="left", pad="0"))
  
new_names <- stations$new_station
names(new_names) <- stations$station
  
stations$station <- stations$new_station

df <- inds_df[[dfnm]]$df[,c("station", "time", "value")]
df$station <- paste0("L", df$station)
df$station <- as.factor(new_names[df$station])
 
df$time <- as.Date(df$time)
```

```{r pres-phi, width=7, height=5}
y <- sort(df$value)
phi <- uba::phi(y=y, phi.parms=uba::phi.control(y))

xx <- data.frame(x=y, phi=phi)

gg1 <- ggplot(xx, aes(x=x, y=phi)) + 
  geom_line() + 
  xlab("") +
  ylab("\u03d5") +
  scale_x_continuous(position = "top") +
  annotate("rect", xmin=0, xmax=max(y), ymin=0.9,ymax=1, alpha=0.2, fill="red") + 
  geom_vline(xintercept= xx[which(xx$phi>=0.9)[1],"x"], linetype="dashed", color="red") +
  theme_minimal()

gg3 <- ggplot(xx, aes(x=1,y=x)) +
  geom_boxplot(position = ) +
  coord_flip() +
  ylab("value") +
  xlab("AAA") +
  theme(panel.background = element_blank(), 
        axis.text.y = element_text(color="white"), 
        axis.ticks.y = element_line(color="white"),
        axis.title.y = element_text(color="white"))

gridExtra::grid.arrange(grobs=list(gg1, gg3), ncol=1, heights=c(4,2))
```

**Figure F.2**: Relevance function and boxplot for PM 2.5 pollution levels in Beijing 


```{r pres-time-series}

min_relev <- xx$x[min(which(xx$phi >= 0.9))]
df2 <- df %>% filter(station %in% unique(station)[2], time >= lubridate::ymd("2014-01-01"))
df2$color <- ifelse(df2$value>=min_relev, "darkred", "black")

ggplot(data = df2, 
       aes(x=time, y=value)) +
  geom_line() +
  geom_point(aes(x=time, y=value, color=color, shape=color, fill=color)) +
  scale_color_manual(values = c("black", "darkred"), guide="none") +
  scale_fill_manual(values = c("black", "darkred"), guide="none") +
  scale_shape_manual(values=c(20, 15), guide="none") +
  annotate("rect", xmin=as.Date("2013-12-31"), xmax=as.Date("2014-02-09"), #ymin=250.5, 
           ymin=min_relev, ymax=500, fill="red", alpha=0.2) +
  theme_minimal()
```

**Figure F.3**: Time series of PM 2.5 pollution levels at a Beijing station

```{r, include=F}
library(uba)
```


```{r pres-util-isometrics}
pc <- uba::phi.control(y)
loss <- uba::loss.control(y)
uP <- uba::util.control(p=0.5)

uba::util.isometrics(y,phi.parms=pc,loss.parms=loss,util.parms = uP)
```


**Figure F.4**: Utility isometrics for relevance function in Fig. F.2